Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-30 Papers/ms.tex
linking sentence

In Figure~\ref{fig:simdata_masses}, we plot the joint posterior distribution
for the SIE mass within its critical ellipse and the total substructure mass
over the entire domain. As one would expect, there is a strong dependence
between these two quantities in the posterior distribution, as mass in the
SIE can be traded off with mass in substructures to some extent, while
the model remains (loosely speaking) ``consistent with the data''.

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{simdata_masses.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures.\label{fig:simdata_masses}}
\end{center}
\end{figure}

>>>>

We do not address the question of exactly which quantities related to the
\density profile of the lens are most scientifically interesting. Nevertheless,
we can verify that the results of the inference do behave in understandable
ways. For example, in Figure~\ref{fig:simdata_masses},
we plot the joint posterior distribution
for the SIE mass within its critical ellipse and the total substructure mass
over the entire domain. As one would expect, there is a strong dependence
between these two quantities in the posterior distribution, as mass in the
SIE can be traded off with mass in substructures to some extent, while
the model remains (loosely speaking) ``consistent with the data''.
\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{simdata_masses.pdf}
\caption{The joint posterior distribution for the SIE mass (integrated within
its critical ellipse, which is not the critical curve of the lens overall),
and the total mass in substructures.\label{fig:simdata_masses}}
\end{center}
\end{figure}
